Fast Hyperparameter Selection for Graph Kernels via Subsampling and\\Multiple Kernel Learning

### 2017-02-06 paper.tex
dadam

\begin{lstlisting}
Input: training matrix (*$\XX$*), list of kernel functions (*$L$*)
(*$\XXs$*) (*$\leftarrow$*) subset_of((*$\XX$*))
(*$K_\textsc{s}$*) (*$\leftarrow$*) [ker_funct((*$\XXs$*)) for ker_funct in (*$L$*)] #matrices on (*$\XXs$*)
(*$\boldsymbol{\eta}$*) (*$\leftarrow$*) EasyMKL((*$K_\textsc{s}$*)) #weights of the functions in L
(*$L_{\textsc{top}}$*) (*$\leftarrow$*) top_of((*$L,\boldsymbol{\eta}$*)) #get the top functions
(*$KL$*) (*$\leftarrow$*) [ker_funct((*$\XX$*)) for ker_fun in (*$L_{\textsc{top}}$*)] #top matrices on (*$\XX$*)
\end{lstlisting}

>>>>

\begin{lstlisting}
Input: examples (*$Tr$*), list of kernel functions (*$L$*),
kernel percentage (*$p_K$*), example percentage (*$p_S$*) 
Output: a list of Gram matrices on (*$Tr$*)
(*$S$*) (*$\leftarrow$*) random_subset_of((*$Tr, p_S$*))
(*$K_\textsc{s}$*) (*$\leftarrow$*) [Gram(*$(S,k)$*) for k in (*$L$*)] #Gram matrices on (*$Tr_s$*)
(*$\boldsymbol{\eta}$*) (*$\leftarrow$*) EasyMKL((*$K_\textsc{s}$*)) #weights of the functions in (*$L$*)
(*$L_{\textsc{top}}$*) (*$\leftarrow$*) top_of((*$L,\boldsymbol{\eta}, p_K$*)) #get the top functions
Return [Gram((*$Tr,k$*)) for k in (*$L_{\textsc{top}}$*)] #top Gram matrices on (*$Tr$*)
\end{lstlisting}
